{\Large \bf Analysing time course microarray data using Bioconductor: a case study using yeast2 Affymetrix arrays}

### 2016-01-25 paper.Rnw
Missing speech marks

<<eval=FALSE,tidy=FALSE>>=
##From Bioconductor
biocLite(c('ArrayExpress', 'Mfuzz, 'timecourse', 'yeast2.db', 
    'yeast2probe', 'yeast2cdf', aAffyPLM'))
##From cran
install.packages(c('GeneNet', 'gplots'))
@

>>>>

<<eval=FALSE,tidy=FALSE>>=
##From Bioconductor
biocLite(c('ArrayExpress', 'Mfuzz', 'timecourse', 'yeast2.db', 
    'yeast2probe', 'yeast2cdf', 'aAffyPLM'))
##From cran
install.packages(c('GeneNet', 'gplots'))
@
